The Free-play Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-06 paper.tex
Update dataset with paragraph duration

TODO: percentage faces seen?

@@

>>>>

Over the dataset, the children faces are detected on 98\% of the images, which
validates the location of the camera and the children to use the cameras to obtain
facial social features.

@@

\todo{Check paragrap}
Figure \ref{fig|durations} presents an histogram of the durations of the
interactions for the two conditions. In the child-child condition, we can
observe two peaks, one around 10 to 15 minutes and one at 40 minutes, the
maximum allowed by the protocol. This indicates that the task is engaging for
the children and encourage them to play with each other for a consequent amount
of time and provides opportunities to display the social behaviours we aimed to
observe with it. In the child-robot condition, the peak at 40 minutes does not
appear (3 children play alongside the robot until the end of the time
allocated). The non-social robot appears to be less engaging than another child
but still elicit plays of an average duration of 19.2 minutes which both is
long enough to display social behaviours, and leaves us space for improvements
if the robot policy is more social.
